Identifying Drawings with the Quick Draw Challenge

### 2018-12-01 report/report_draft.Rmd
update report

---
title: "Identifying Drawings with the Quick Draw Challenge"
author: "Blue Team"
output: 
  pdf_document:
    keep_tex: yes
bibliography: references.bib
---

@@

# Theory & Literature Review

CNN with dilation is preferable to LSTM because it's presumably
faster. We can cite some papers here.

# Hypotheses

@@

$H_a:$ Prediction will go up when we use regularization

# Data

We got our data from Google/Kaggle

@@

>>>>

---
title: "Identifying Drawings with the Quick Draw Challenge"
author: "Group 3"
output: 
  pdf_document:
    keep_tex: yes
bibliography: references.bib
---

@@

# Introduction

Our team has based our project idea on the "Quick, Draw!" Kaggle competition 
which classifies user drawings into one of 345 label categories. Many drawings 
were incomplete or failed to match the label. The challenge was to effectively 
build a recognizer that could work with this noisy data. The challenge was unique 
from an algorithmic perspective because the data included both temporal and 
spatial components; areas that have traditionally used two different 
types of Neural Network Architectures. Our team attempted to provide a solution 
using a subset of the data, to the Kaggle problem, while taking a more in depth 
look at potential pitfalls and modeling strategy, without having to use 
extensive computational resources.

# Methods

First, we got our data from Google/Kaggle. CNNs are traditionally known to work
well with spatial data, which prompted us to process the original csv files to 
images of the drawings.

@@

$H_a:$ Prediction will go up when we use regularization.

$H_a:$ Run neural networks without any activations.

$H_a:$ Try different architectures- number of layers, different (or no) 
activations

$H_a:$ CNN with dilation is preferable to LSTM because it's presumably
faster. We can cite some papers here.

@@

# Appendix

Add computer code, plots, and other relevant technical details that will help
me evaluating your work.

# Statement of contribution
